### 2020-05-26 writeup/transfer.tex
add label

Theorem \ref{thm_main_informal} shows nearly tight bounds on the trade-off between model-shift bias and variance reduction.
%determined by the covariate shift matrix and the model shift.
The bounds get tighter and tighter as $\rho_1$ increases.
A formal version of Theorem \ref{thm_main_informal} is presented in Theorem \ref{thm_model_shift} and its proof is presented in Appendix \ref{app_proof_main}.

\textbf{Second setting: Many tasks with the same covariates.}
We extend the above result to any number of tasks that have the same covariates.
%In this section we consider the setting with $k$ many that have the same covariates.
Since the tasks all have the same number of datapoints and covariance matrix, the trade-off between model shift bias and variance will be captured by their task models $\set{\beta_i}_{i=1}^k$.
%For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p\times k}$ denote the underlying task model parameters.
We derive the model shift bias and variance in the following result.

>>>>

Theorem \ref{thm_main_informal} shows nearly tight bounds on the trade-off between model-shift bias and variance reduction.
%determined by the covariate shift matrix and the model shift.
The bounds get tighter and tighter as $\rho_1$ increases.
A formal version of Theorem \ref{thm_main_informal} is presented in Theorem \ref{thm_model_shift} and its proof is presented in Appendix \ref{sec_pfmain}.

Our second result applies to the set setting of many tasks with the same covariates.
%We extend the above result to any number of tasks that have the same covariates.
%In this section we consider the setting with $k$ many that have the same covariates.
Since the tasks all have the same number of datapoints and covariance matrix, the trade-off between model shift bias and variance will be captured by their task models $\set{\beta_i}_{i=1}^k$.
%For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p\times k}$ denote the underlying task model parameters.
We can also derive a tight trade-off between model shift bias and variance reduction for this setting.
The formal statement is stated in Theorem \ref{thm_many_tasks} and its proof can be found in Appendix \ref{app_proof_many_tasks}.
